conmat: generate synthetic contact matrices for a given age-stratified population

### 2024-08-16 paper/paper.Rmd
pushing partial prediction helpers

@@

```{r}
#| label: load-conmat
library(conmat)
tasmania <- abs_age_state("TAS")
tasmania
```

@@

```{r}
# Show partial dep plot of the six main covariates
```

@@

When the six covariates are added up together for each setting (in other words, each model) and exponentiated, they show the following patterns:

>>>>

```{r}
#| label: libraries
library(purrr)
library(patchwork)
library(conmat)
library(ggplot2)
```

@@

```{r}
#| label: abs-age
tasmania <- abs_age_state("TAS")
tasmania
```

@@

```{r}
#| label: partial-plots
#| echo: FALSE
fit_home <- polymod_setting_models$home
age_grid <- create_age_grid(ages = 1:99)
term_names <- extract_term_names(fit_home)
term_var_names <- clean_term_names(term_names)
age_predictions <- predict_individual_terms(
  age_grid = age_grid,
  fit = fit_home,
  term_names = term_names,
  term_var_names = term_var_names
)

age_predictions_all_settings <- map_dfr(
  .x = polymod_setting_models,
  .f = function(x) {
    predict_individual_terms(
      age_grid = age_grid,
      fit = x,
      term_names = term_names,
      term_var_names = term_var_names
    )
  },
  .id = "setting"
)

plot_age_term_settings <- gg_age_terms_settings(age_predictions_all_settings)
age_predictions_long <- pivot_longer_age_preds(age_predictions)
# this is a figure we want
plot_age_predictions_long <- gg_age_partial_pred_long(age_predictions_long) +
  coord_equal() +
  labs(x = "Age from",
       y = "Age to")

age_predictions_long_sum <- add_age_partial_sum(age_predictions_long)
# this is a figure we want
plot_age_predictions_sum <- gg_age_partial_sum(age_predictions_long_sum) + coord_equal() +
  labs(x = "Age from",
       y = "Age to")
# this is a figure we want
```

```{r}
#| echo: FALSE
#| fig.height: 8
plot_all_terms_sum <- plot_age_predictions_long +
  plot_age_predictions_sum + 
  plot_layout(design = "
            A
            A
            A
            A
            A
            A
            A
            B
            ") + 
  plot_annotation(
    tag_levels = "A"
  )

plot_all_terms_sum
```

@@

When the six covariates are added up together for each setting (in other words, each model), then exponentiated, they show the following patterns:
